Nail: A practical interface generator for data formats

### 2014-04-02 paper/concl.tex
Conclusion, eval, future work

\section{Conclusion}

This paper presented the initial design and implementation of
\textit{Nail}, an XXX...

>>>>

\section{Conclusion}
\label{s:concl}
This paper presented the initial design and implementation of \textit{Nail}, a usable interface
generator for data formats. Nail allows programmers to avoid memory corruption and ambiguity
vulnerabilities while reducing effort in parsing and generating real world protocols and file
formats. We have demonstrated Nail's expressive power by implementing DNS and Ethernet.

Our code is open source on GitHub\footnote{\url{https://github.com/jbangert/nail/}}.

### 2014-04-02 paper/eval.tex
Conclusion, eval, future work

Furthermore, our GitHub\footnote{\url{https://github.com/jbangert/nail/tree/master/examples}}
repository contains other Nail grammars, such as a TAP network stack that processes Ethernet, ARP,
ICMP, IP and UDP and the grammar for Nail itself.

>>>>

Furthermore, our GitHub
repository contains other Nail grammars, such as a TAP network stack that processes Ethernet, ARP,
ICMP, IP and UDP and the grammar for Nail itself.

### 2014-04-02 paper/future.tex
rough intro pass done, with some sizable holes left
Conclusion, eval, future work

\section{Future work}

The Nail parser generator is work in progress and feedback of all sorts is heavily
encouraged. Source code is available upon request and will be released publicly pending clean-up and
maturity. Short-term future work will include improving the scoping of dependency fields and adding
support for offset fields.

A major problem with the current design of Nail is that the design of the grammar dictates the
interna structure of the software. This makes changing grammars or adding Nail to existing software
awkward. One possible solution to this problem would be to implement a concept similar to Relational
Lenses~\cite{bohannon2006relational}, which would allow  the data model to be 'seen' by
the rest of the program through an isomorphism. Such an isomorphism would still be much more concise
than two sets of semantic actions, while allowing changes in syntax, alternative representations
and adaption to legacy systems.

>>>>

\section{Future work}
\label{s:future}

The Nail parser generator is work in progress and feedback of all sorts is heavily
encouraged.

A major problem with the current design of Nail is that the design of the grammar dictates the
internal structure of the software. This makes changing grammars or adding Nail to existing software
awkward. One possible solution to this problem would be to implement a concept similar to Relational
Lenses~\cite{bohannon2006relational}, which would allow  the data model to be 'seen' by
the rest of the program through an isomorphism. Such an isomorphism would still be much more concise
than two sets of semantic actions, while allowing changes in syntax, alternative representations
and adaption to legacy systems.
